Title

### 2024-05-12 paper/main.tex
Updates

\begin{abstract}
	\emph{Causal Discovery} is the process of learning the causal structure
	either in form of a Directed Acyclic Graph (DAG) or a Structural
	Equation Model (SEM) from observational data. This problem has been
	extensively studied for both DAGs and SEMs.
	In the field of DAGs, many automated algorithms
	have been developed for constructing a DAG from a given dataset. However, the
	adaption of these algorithms in applied fields have been limited,
	possibly due to a lack of confidence in these algorithms stemming from
	them making obvious mistakes, and the difficulties in choosing the
	right algorithm for a given dataset. Consequently, in applied
	disciplines, these DAGs are predominantly constructed manually based on
	domain expertise. Due to being constructed by hand, it is vital that
	the fit of these models are tested against data and the models are
	potentially modified to acheive a better fit. On the other hand, in the
	field of SEMs models are typically constructed manually through an
	iterative process of assessing fit and modifying the model according to
	that. This process is commonly known as \emph{Specification Search} 
	where methods like \emph{modification indices} can be used to guide this
	modification process. In the case of DAGs, although there are tests
	such as Shipley 2000 that can assess the global fit of model by
	combining the tests using implied conditional independencies of the model, but
	there are no methods that can guide our modification process. In this
	paper, we present a simple modification process aimed at helping researchers
	in manually constructing or modifying the DAGs outputted by an algorithm.
	This modification process is based on using a measure of association for 
	these individual local CI tests to identify the worst offending CI test and
	combining it with expert knowledge. We also present a measure of
	association based on canonical correlations for mixed data. We also
	present a graphical web-tool that can assist researchers in iteratively
	modifying and constructing their DAGs. We theoretically show that in
	the presence of an oracle, this iterative modification process is
	consistent in recovering the true DAG. Emprically, we show that this
	process performs comparably to PC and Hill-Climb Search algorithms if
	the user is able to correctly identify the direction of the edge in one
	out of three cases.
\end{abstract}

@@

\textbf{Para 2: Reasons behind this}

@@

\begin{enumerate}
	\item Biased towards sparse graphs.
	\item Algorithms making obvious mistakes: These algorithms often 
		make very obvious mistakes, making it harder for the user
		to trust them.
	\item Difficulties in choosing an algorithm: For any given dataset, the
		user need to make a choice of the algorithm. Given that these
		algorithms work very differently, it can be difficult to make a
		choice. Additionally, each of these algorithms have
		hyperparameters and choices to make for them, making it
		difficult. As there is no way to evaluate the performance of 
		these algorithms on our dataset.
\end{enumerate}

\textbf{Para 3: Importance of testing, include modification indices}

Both in the cases when the DAG is an output of an algorithm or when constructed
by hand, it is vital to test these models against data before using them for
making any inference. In the field of Structural Equation Models (SEMs)
modification indices have been used to do this. However, as modification index
is an evaluation of the global fit of the model. An alternative is local fit of
models using CI tests where the implied conditional independences of the model
can be tested using statistical tests. Similar to modification indices, these
tests can then be used to modify our models. Figure shows an example of this
testing. We can not also only rely on the p-values, effect size can help in
deciding.

\textbf{Para 4: Mixed data testing}

As these CI based testing uses p-values and effect size measures from CI tests
for testing. And as mixed data is common, we need both a test and effect size
measure for mixed data. Recently, a few CI tests for mixed data have been
proposed but an effect size is still missing.

>>>>

\begin{abstract}
	\emph{Causal Discovery} involves learning causal structures
	from data, typically represented as  Directed Acyclic Graphs
	(DAGs) or Structural Equation Models (SEMs). This problem has been
	extensively studied for both DAGs and SEMs. In the field of DAGs, many
	automated algorithms have been developed for constructing a DAG from a
	given dataset. However, the adaption of these algorithms in applied
	fields have been limited, possibly due to a lack of confidence in these
	algorithms stemming from them making obvious mistakes, and the
	difficulties in choosing the right algorithm for a given dataset.
	Consequently, in applied disciplines, these DAGs are predominantly
	constructed manually based on domain expertise. Due to being
	constructed by hand, it is vital that the fit of these models are
	tested against data and the models are potentially modified to acheive
	a better fit. On the other hand, in the field of SEMs models are
	typically constructed manually through an iterative process of
	assessing fit and modifying the model according to that. This process
	is commonly known as \emph{Specification Search} where methods like
	\emph{modification indices} can be used to guide this modification
	process. In the case of DAGs, although there are tests such as Shipley
	2000 that can assess the global fit of model by combining the tests
	using implied conditional independencies of the model, but there are no
	methods that can guide our modification process. In this paper, we
	present a simple modification process aimed at helping researchers in
	manually constructing or modifying the DAGs outputted by an algorithm.
	This modification process is based on using a measure of association
	for these individual local CI tests to identify the worst offending CI
	test and combining it with expert knowledge. We also present a measure
	of association based on canonical correlations for mixed data. We also
	present a graphical web-tool that can assist researchers in iteratively
	modifying and constructing their DAGs. We theoretically show that in
	the presence of an oracle, this iterative modification process is
	consistent in recovering the true DAG. Emprically, we show that this
	process performs comparably to PC and Hill-Climb Search algorithms if
	the user is able to correctly identify the direction of the edge in one
	out of three cases.
\end{abstract}

@@

\textbf{Para 2: Reasons behind this and importance of verifying against data}

@@

\begin{enumerate}
	\item Biased towards sparse graphs.
	\item Algorithms making obvious mistakes: These algorithms often 
		make very obvious mistakes, making it harder for the user
		to trust them.
	\item Difficulties in choosing an algorithm: For any given dataset, the
		user need to make a choice of the algorithm. Given that these
		algorithms work very differently, it can be difficult to make a
		choice. Additionally, each of these algorithms have
		hyperparameters and choices to make for them, making it
		difficult. As there is no way to evaluate the performance of 
		these algorithms on our dataset.
\end{enumerate}
Both in the cases when the DAG is an output of an algorithm or when constructed
by hand, it is vital to test these models against data before using them for
making any inference.

\textbf{Para 3: Structural Equation Models, testing, include modification indices}

In the field of Structural Equation Models (SEMs)
modification indices have been used to do this. However, as modification index
is an evaluation of the global fit of the model. An alternative is local fit of
models using CI tests where the implied conditional independences of the model
can be tested using statistical tests. Similar to modification indices, these
tests can then be used to modify our models. Figure shows an example of this
testing. We can not also only rely on the p-values, effect size can help in
deciding.

\textbf{Para 4: Measure of Association}
As these CI based testing uses p-values and effect size measures from CI tests
for testing. And as mixed data is common, we need both a test and effect size
measure for mixed data. Recently, a few CI tests for mixed data have been
proposed but an effect size is still missing.
